\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2020-12-15 icra-2021.tex
implementing Hector's and Ulrik's suggestions (3)

\begin{pb}[UAV planning problem]\label{pb}
  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic} and Proposition~\ref{prop:rank}. We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ for the UAV planning problem.
\end{pb}

@@

The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$, to solve Problem~\ref{pb}.

@@

\begin{defn}[Valid control sequence]\label{def:valid}
  A control sequence $\mathbf{u}$ is valid if for every stage $\Gamma_{i-1},\,i\in[l]^+$ if there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$
  \begin{equation}\begin{split}\label{eq:mission-valid}
    \mathbf{u}^a_{k}=\{&\langle\mathbf{c}_{k},\mathbf{s}_{k}\rangle\mid\,\exists n\in\mathbb{Z}_{>0},\\&\langle\varphi_{i-1}(\mathbf{p}_{k-n},\mathbf{c}_{k-n}),\Psi(\mathbf{s}_{k-n})\rangle\in\mathcal{M}_{i-1}\\
    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k},\mathbf{c}_{k}),\Psi(\mathbf{s}_{k})\rangle\in\mathcal{M}_{i}\}.
  \end{split}\end{equation}
\end{defn}

Let us proof that if the mission is valid, the instantaneous energy consumption can be modeled as linear combination of the state from the Equation~(\ref{eq:state-perf}).

\begin{thm}[Periodic energy model]\label{thm:state-vs-energy}
  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}. Assume Assumption~\ref{assm:periodic} holds, the model of Equation~(\ref{eq:state-perf}) behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state $\mathbf{q}_0$ is $y_0^a/m$ for the first coefficient where $y_0^a\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^a$ can be the initial measurement or the measurement from a previous instance of the algorithm}, $(1/2)y_0^a/m$ for all the others, and the mission is valid.
  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$.
\end{thm}
\begin{proof}
  The proof is based on mathematical induction. 
  Base case: we proof that $y_0=y_0^a$. Recall the definition of the state in Equation~(\ref{eq:state-details}). The output is $y_{0}=\alpha_{0,0}+\alpha_{0,1}+\dots+\alpha_{0,r}=y_0^a/m+(1/2)y_0^a/m+\cdots+(1/2)y_0^a/m=y_0^a$.

>>>>

\begin{pb}[UAV planning problem]\label{pb}
  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic} and Proposition~\ref{prop:rank}.

  We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and to derive the path resulting from such plan for the UAV planning problem.
\end{pb}

@@

The main purpose of the algorithm is to output a valid control sequence $\mathbf{u}:=\{\mathbf{u}_0,\mathbf{u}_1,\dots\}$ at each time step given an initial plan $\Gamma$ and to direct the UAV on a valid path: to solve Problem~\ref{pb}.

\begin{defn}[Valid control sequence and path]\label{def:valid}
  A \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[l]^+$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.

  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path}
  \begin{equation}\begin{split}\label{eq:mission-valid}
   \mathcal{P}:=\{\mathbf{p}_k\mid&\,\exists \mathbf{u}_k,n\in\mathbb{Z}_{>0},\\
    &\langle\varphi_{i-1}\left(\mathbf{p}_{k-n}\right),\mathbf{u}_{k-n}\rangle\in\Gamma_{i-1}\\
    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle\in\Gamma_i\},
  \end{split}\end{equation}
  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k,1},\dots,$ $c_{k,\rho}),c_{k,\rho+1},\dots,c_{k,\rho+\sigma}\rangle$.
\end{defn}

Let us proof that the plan is periodic and one period is valid, then the plan is valid.

\begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
?

@@

  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}. Assume Assumption~\ref{assm:periodic} holds, the model of Equation~(\ref{eq:state-perf}) behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state $\mathbf{q}_0$ is $y_0^a/m$ for the first coefficient where $y_0^a\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^a$ can be the initial measurement or the measurement from a previous instance of the algorithm}, $(1/2)y_0^a/m$ for all the others, and the mission is valid.
  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$.
\end{thm}
\begin{proof}
  The proof is based on mathematical induction. 
  Base case: we proof that $y_0=y_0^a$. Recall the definition of the state in Equation~(\ref{eq:state-details}). The output is $y_{0}=\alpha_{0,0}+\alpha_{0,1}+\dots+\alpha_{0,r}=y_0^a/m+(1/2)y_0^a/m+\cdots+(1/2)y_0^a/m=y_0^a$.
